Illustrating splines using the diamond pricing dataset

### 2024-06-29 text/01/impact-of-population-size.Rmd
Work on stash-files

```{r, echo=FALSE}
df <- data.frame(sample_size=c(50, 200, 4000))
df$fpc_pop_ten_thousand <- sqrt((10000-df$sample_size)/(9999))
df$fpc_pop_ten_million <- sqrt((10000000-df$sample_size)/(9999999))
df
```

>>>>

```{r fpc, echo=FALSE}
df <- data.frame(sample_size=c(50, 200, 4000))
df$fpc_pop_ten_thousand <- sqrt((10000-df$sample_size)/(9999))
df$fpc_pop_ten_million <- sqrt((10000000-df$sample_size)/(9999999))
df
```

### 2024-06-29 text/24/diamond-spline.Rmd
Work on stash-files

```{r initialization, echo=FALSE}
library(broom)
library(pspline)
library(readr)
library(rms)
library(tidyverse)
library(yaml)
f0 <- "https://raw.githubusercontent.com/pmean/datasets/master/"
f1 <- "diamonds.yaml"
dd <- read_yaml(paste0(f0, f1))
```

@@

```{r read-diamonds}
f2 <- "diamonds.txt"
raw_data <- read.fwf(file=paste0(f0, f2), widths=c(5,2,5,4,5))
di <- raw_data
names(di) <- c(
  "carat",
  "colour",
  "clarity",
  "certification",
  "price"
)
```

>>>>

```{r initialization, echo=FALSE}
library(broom)
library(glue)
library(pspline)
library(readr)
library(rms)
library(tidyverse)
library(yaml)

f0 <- "https://raw.githubusercontent.com"
f1 <- "pmean/datasets/master"
f2 <- "singapore-diamond-prices.yaml"

dd <- read_yaml(glue("{f0}/{f1}/{f2}"))
```

@@

```{r read-diamonds}
f2 <- "singapore-diamond-prices.txt"
raw_data <- read.fwf(
  file=glue("{f0}/{f1}/{f2}"), 
  widths=c(5,2,5,4,5))
di <- raw_data
names(di) <- c(
  "carat",
  "colour",
  "clarity",
  "certification",
  "price"
)
```
